Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-13 Ben_Manuscripts/structure_paper/Draft.tex
More draft edits and figure updates

			\begin{subfigure}{\textwidth}
			\centering
		    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			        %\caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
        %MRS7: be consistent on capitalization
	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
	experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
	disordered basin (d) Parallel Displaced, ordered basin and (e) Parallel Displaced, disordered basin 
	configurations with (c) experimental WAXS. Quantitative comparisons of the relative 
	intensities of reflections of interest are present in Table~\ref{table:relative_inensities_300K}. 
	In all cases, R-double is not present.}~\label{fig:XRDsim} 
        %MRS7: may need to make clearer the differences between the simulated structures. I think its worth pointing out
        %that although rdouble isn't there, for the more structured ones, there is a 7.4 band, even if it disappears at q=0.
  \end{figure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type
  %MRS7: huh.
  There are clear differences between simulated and experimental results that must be addressed
  and justified. We will explore the possible origin of each experimental reflection and form 
  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
  want answer:  
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

@@

@@

@@

%MRS7: couple -> ``two main''?
%MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
  There are two reasons why we see stronger ordered chain packing at 280 K compared to
  experimental conditions of 300 K.
  \begin{enumerate}
  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
  		may not correctly model the behavior of the tails at 300 K (citation?).
                % look for papers on protien folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
  		to pack between vertically adjacent monomer tails. In our case, the tail region is
  		less dense than experiment which gives the tails freedom to organize in a more
  		entropically favored disordered state. 
  \end{enumerate}

@@

%MRS7: not a strong thesis sentence. 
  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). We used this 
  information to understand how far apart monomers stack within monomer columns and
  the degree to which they are correlated.

@@

@@

  The correlation length between stacked monomer head groups of the ordered systems also show
  closer agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
  not extract a reliable correlation length from the disordered parallel displaced configuration
  since the peaks do not show clear patterns than can easily be fit to exponential decay.
  %The amount of noise in the correlation function and the lack of an initial peak suggests that 
  %the correlation length is less than $\mathit{d}_{equil}$.
  In general, we see that correlation length increases as monomers stack closer together. The same
  trend has been seen in molecular dynamics studies of polymer fluids~\cite{koshy_density_2003}.
  We hypothesize that the correlation length of the sandwiched configuration would increase to a
  value near experiment if monomers packed closer together.

@@

  %MRS7: question - pushing Matt on this, he seemed to imply that the high value of the peaks indicated large
  %LOCAL ordering, and that defects/misaligned pores would give rise to BROADENING, but wouldn't change the 
  %intensity of the peaks that much.  If so, this isn't a great explanation. 
  The simulated intensity of R-$\pi$ is also more intense than experiment because our system
  models near-perfectly straight pores with no defects. Nearly all of the intensity in 
  R-$\pi$ of our simulated patterns is concentrated at a single point. Figure~\ref{fig:simulated_adjusted_colorbar}
  shows the simulated pattern of the ordered sandwiched configuration with the upper boundary
  on the colorbar adjusted to be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only
  distinguishable reflections are those of R-$\pi$ and R-pores. In the experimental pattern 
  (Figure~\ref{fig:experimental_adjusted_colorbar}), the intensity is more evenly spread out
  over all of R-$\pi$. 
  % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
  % out what to do about it
  % BJC5: Could it also be related to noise in xy direction?
  % BJC5 : I think my original intent was to explain it as tortuosity. But it's not clear if the
  % reflection is arced

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
	  \caption{}\label{fig:simulated_adjusted_colorbar}
  \end{subfigure}
  \begin{subfigure}{0.4\textwidth}
	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
	  \caption{}\label{fig:experimental_adjusted_colorbar}
  \end{subfigure}
  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
  simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
  higher than all other plots.}\label{fig:intense_rpi}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
%	\label{fig:rotated_carboxylate}
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered.png}
	\label{fig:staggered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers.png}
  	\label{fig:rotated_monomers}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.png}
  	\label{fig:solvated_pore}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
%  	\label{fig:rotated_carboxylate_rzplot_restrained}
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
  	\label{fig:staggered_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
  	\label{fig:rotated_monomers_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
  	\label{fig:solvated_pore_rzplot_restrained}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
%  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
%  	%BJC4: needs to run longer
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png} %BJC5: this needs to be updated
  	\caption{}\label{fig:staggered_rzplot_norestraints} 
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.png}
  	\caption{}\label{fig:solvated_pore_rzplot_norestraints}
  \end{subfigure}
  \caption{R-double is present in all three initial configurations tested while the heavy atoms
  in the headgroup are held in place with position restraints. R-double fades once 
  the position restriants are released.}\label{fig:rdouble}
  \end{figure}

  R-double appears in the solvated system due to the structure of the head groups. To prove this,
  we removed the head groups from the trajectory used to produce Figure~\ref{fig:solvation}a 
  in order to produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear
  without the influence of the head groups. Water molecules must play a role in the structuring
  of the head groups since R-double does not appear in any dry simulations.

  When two vertically stacked monomer head groups hydrogen bond with a shared water 
  molecule, the monomers are drawn closer together (as illustrated in 
  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
  with a head group below itself, it will be less likely to share a water molecule 
  with a head group above it due to steric constraints. The monomer head group above
  can just as easily share a water molecule with a head group above itself. In this scenario,
  the centers of each group are 2 times the $\pi$-stacking distance apart which would
  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
  Peaks in the distributions represent the scenario where a monomer head group shares a 
  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
  we calculated the discrete fourier transform of the distributions which we used as a rough 
  indicator of whether the head group arrangement will lead to R-double. We see the 
  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.

  The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
  thermotropic Col\textsubscript{h} phases. Rather, they were very low water content 
  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
  This detail may be important for reproducing the results of Feng et al.

%MRS7: probably want to say that this is a likely mechanism, if it can
%occur with the given forcefield, since we had a hard time identifying any others. A more realistic forcefield
% may make the effect stronger.

  % Combine all of these figures
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
%  \caption{Full system}\label{fig:rdouble_offset}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
%  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
%  \end{subfigure}
%  \caption{The structure of the head groups is responsible for the appearance of
%  R-double in (a). Removing head groups from the trajectory results in a simulated 
%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
%  \end{figure}
%  
%  \begin{figure}[!htb]
%  \centering
%  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
%  % to the floating head groups)
%  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
%  drawn closer together. Head groups with blue bonds were stacked above those 
%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
%  \end{figure}
%  
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{pore_hbonds.png}
%  \caption{}\label{fig:pore_hbonds}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
%  \caption{}\label{fig:pore_hbonds_ft}
%  \end{subfigure}
%  %MRS7: add a bit more explanation - no description of discrete FT.
%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
%  shared hydrogen bonded water molecule between a monomer head group and that stacked
%  vertically above it. (b) }\label{fig:hbond_quantification}
%  \end{figure}

  \begin{figure}[!htb]
  \begin{subfigure}{0.45\textwidth}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
  \caption{Full system}\label{fig:rdouble_offset}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
  \end{subfigure}
  \caption{}\label{fig:rdouble_origin}
%  \caption{The structure of the head groups is responsible for the appearance of
%  R-double in (a). Removing head groups from the trajectory results in a simulated 
%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
  % to the floating head groups)
  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
  \caption{}\label{fig:hbond_visualization}
%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
%  drawn closer together. Head groups with blue bonds were stacked above those 
%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds.png}
  \caption{}\label{fig:pore_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
  \caption{}\label{fig:pore_hbonds_ft}
  \end{subfigure}
  \caption{}\label{fig:hbond_quantification}
  %MRS7: add a bit more explanation - no description of discrete FT.
%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
%  shared hydrogen bonded water molecule between a monomer head group and that stacked
%  vertically above it. (b) }\label{fig:hbond_quantification}
  \caption{}\label{fig:figure}
  \end{figure}

@@

@@

  %MRS7: this section reads a little bit as ``and then, and
  %then''. Think how to make it more focused on core ideas to communicate. Thes is they are all about the same. Perhaps should be the beginning of the section?

>>>>

			\begin{subfigure}{\textwidth}
			\centering
		    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			        %\caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
        %MRS7: be consistent on capitalization
	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
	experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
	disordered basin (d) Parallel Displaced, ordered basin and (e) Parallel Displaced, disordered basin 
	configurations with (c) experimental WAXS. Quantitative comparisons of the relative 
	intensities of reflections of interest are present in Table~\ref{table:relative_inensities_300K}. 
	In all cases, R-double is not present.}~\label{fig:XRDsim} 
        %MRS7: may need to make clearer the differences between the simulated structures. I think its worth pointing out
        %that although rdouble isn't there, for the more structured ones, there is a 7.4 band, even if it disappears at q=0.
        %BJC6: 7.4 band is any parallel displaced configuration, not more structured systems.
  \end{figure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type
  %MRS7: huh.
  %BJC6: yea, specifically the one for j phys chem B. I compiled with a different document type and the captions looked normal
  There are clear differences between simulated and experimental results that must be addressed
  and justified. We will explore the possible origin of each experimental reflection and form 
  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
  want answer:  
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

@@

  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Obtaining an equilibrium structure at a precise temperature is
  a challenge that force fields often fail to overcome. Wang et al. highlighted the 
  shortcoming of some of the most popular protein force field in predicting the temperature
  dependence of protein structural ensembles \cite{wang_building_2017}. It is possible that   % page 12
  our membrane system, simulated at 300K, does not fully represent the true structure at 300K.

@@

% BJC6 : added better justification to beginning of section
%  %MRS7: couple -> ``two main''?
%%MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
%  There are two reasons why we see stronger ordered chain packing at 280 K compared to
%  experimental conditions of 300 K.
%  \begin{enumerate}
%  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
%  		may not correctly model the behavior of the tails at 300 K (citation?).
%                % look for papers on protien folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
%  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
%  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
%  		to pack between vertically adjacent monomer tails. In our case, the tail region is
%  		less dense than experiment which gives the tails freedom to organize in a more
%  		entropically favored disordered state. 
%  \end{enumerate}

@@

@@

  There is not a single reason for the high intensity of R-$\pi$ in our simulations.
  We used one-dimensional pair distribution functions of the centers of masses of monomer
  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
  columns and the degree to which they are correlated. These metrics helped us disect the 
  various contributions to R-$\pi$. Figure ~\ref{fig:correlation} shows $g(z)$ for all 
  systems tested.

%  The first peak of $g(z)$ is larger in the ordered
%  basin systems compared to those in the disordered basin. This observation is indicative
%  of a higher degree of local ordering in the ordered basin systems which causes an
%  increase in the intensity of R-$\pi$.

  %MRS7: not a strong thesis sentence.
%  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
%  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). We used this 
%  information to understand how far apart monomers stack within monomer columns and
%  the degree to which they are correlated.

@@

  %We expect that when monomers stack closer together, steric clashes
  %force head groups to orient in a more ordered fashion. If head groups in our model stayed 3.7 \AA
  %apart, we may actually see higher values of R-$\pi$ due to enhance order.

@@

  The correlation length of the parallel displaced, ordered basin system shows
  the closest agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
  not extract a reliable correlation length from the disordered parallel displaced configuration
  since the peaks do not show clear patterns that can easily be fit to exponential decay. The 
  correlation length of both sandwiched systems is relatively low because the height of the first
  peak of $g(z)$ is so high. The peak height indicates the degree of local ordering and influences
  the intensity of R-$pi$. If vertically adjacent sandwiched head groups were less ordered, which
  might be achieved with much longer simulations, then the leading peak intensity should decrease and
  the correlation length would increase. We expect that the leading peak would only get more intense 
  if monomers stacked 3.7 \AA apart. Conversely, parallel displaced head groups are not as confined
  by their vertically adjacent neighbors. This z-direction translational freedom may still be 
  feasible if monomers stack 3.7 \AA apart in a parallel displaced configuration.

  %The amount of noise in the correlation function and the lack of an initial peak suggests that 
  %the correlation length is less than $\mathit{d}_{equil}$.
  %BJC6: not supported by data vv
%  In general, we see that correlation length increases as monomers stack closer together. The same
%  trend has been seen in molecular dynamics studies of polymer fluids~\cite{koshy_density_2003}.
%  We hypothesize that the correlation length of the sandwiched configuration would increase to a
%  value near experiment if monomers packed closer together.

@@

  %MRS7: question - pushing Matt on this, he seemed to imply that the high value of the peaks indicated large
  %LOCAL ordering, and that defects/misaligned pores would give rise to BROADENING, but wouldn't change the 
  %intensity of the peaks that much.  If so, this isn't a great explanation. 
  %BJC6: worked this into other paragraphs. I find this paragraph awkward and the figure unnecessary.
%  The simulated intensity of R-$\pi$ is also more intense than experiment due to strong local
%  ordering. Nearly all of the intensity in R-$\pi$ of our simulated patterns is concentrated 
%  at a single point. Figure~\ref{fig:simulated_adjusted_colorbar} shows the simulated pattern
%  of the ordered sandwiched configuration with the upper boundary on the colorbar adjusted to
%  be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only distinguishable reflections
%  are those of R-$\pi$ and R-pores. In the experimental pattern 
%  (Figure~\ref{fig:experimental_adjusted_colorbar}), the intensity is more evenly spread out
%  over all of R-$\pi$. 
  % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
  % out what to do about it
  % BJC5: Could it also be related to noise in xy direction?
  % BJC5 : I think my original intent was to explain it as tortuosity. But it's not clear if the
  % reflection is arced

  %BJC6: not sure if this should go in supplemental
%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.4\textwidth}
%	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
%	  \caption{}\label{fig:simulated_adjusted_colorbar}
%  \end{subfigure}
%  \begin{subfigure}{0.4\textwidth}
%	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
%	  \caption{}\label{fig:experimental_adjusted_colorbar}
%  \end{subfigure}
%  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
%  the simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
%  higher than all other plots.}\label{fig:intense_rpi}
%  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
%	\label{fig:rotated_carboxylate}
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered.png}
	\label{fig:staggered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers.png}
  	\label{fig:rotated_monomers}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.png}  %BJC6: I can simplify this more (stacked monomers on each side with a few water molecules in between.
  	\label{fig:solvated_pore}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
%  	\label{fig:rotated_carboxylate_rzplot_restrained}
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
  	\label{fig:staggered_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
  	\label{fig:rotated_monomers_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_pore_rzplot_restrained.png}
  	\label{fig:solvated_pore_rzplot_restrained}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
%  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
%  	%BJC4: needs to run longer
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png} %BJC5: this needs to be updated
  	\caption{}\label{fig:staggered_rzplot_norestraints} 
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.png}
  	\caption{}\label{fig:solvated_pore_rzplot_norestraints}
  \end{subfigure}
  \caption{(a) When monomers are non-uniformly spaced (top), R-double appears if all heavy atoms
  of the head groups are held in place with position restraints (middle). R-double quickly fades once 
  the position restraints are released (bottom). (b) When monomer head groups are rotated with respect
  to vertically adjacent monomers (top), R-double is visible while the heavy atoms of the head groups
  are held in place with position restraints (middle). Again, R-double fades once the position 
  restraints are released. (c) When we add 1 wt\% water to the parallel displaced configuration in the
  ordered basin (top) R-double is not initially present during the restrained portion of equilibration (middle).
  After 200 ns of equilibration, R-double becomes visible and persists for another 200 ns (bottom).}\label{fig:rdouble}
  \end{figure}

  R-double appears in the solvated system due to the structure of the head groups. To prove this,
  we removed the head groups from the trajectory used to produce Figure~\ref{fig:solvated_pore_rzplot_norestraints}
  in order to produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear
  without the influence of the head groups. Water molecules must play a role in the structuring
  of the head groups since R-double does not appear in any dry simulations.

  When two vertically stacked monomer head groups hydrogen bond with a shared water 
  molecule, the monomers are drawn closer together (as illustrated in 
  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
  with a head group above itself, it will be less likely to share a water molecule 
  with a head group below it due to steric constraints. The monomer head group below
  can just as easily share a water molecule with a head group below itself. In this scenario,
  the centers of each pair are 2 times the $\pi$-stacking distance apart which would
  lead to R-double (much like the configuration in Figure~\ref{fig:staggered_rzplot_norestraints}). There are
  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
  Peaks in the distributions represent the scenario where a monomer head group shares a 
  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
  we calculated the discrete fourier transform of the distributions which we used as a rough 
  indicator of whether the head group arrangement will lead to R-double. We see the 
  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.

  It is likely that R-double originates from water molecules as described above and it is the 
  only mechanism that occurred without using position restraints. The extent of the hydrogen
  bonding network that forms is largely determined by the accuracy of the forcefield. It is 
  possible that a more realistic forcefield would make the effect stronger or weaker. If 
  this is truly the mechanism, it implies that the systems studied by Feng et 
  al.\cite{feng_scalable_2014,feng_thin_2016} were not truly thermotropic Col\textsubscript{h}
  phases. Rather, they were very low water content H\textsubscript{II} phases unintentionally
  created due to the neat monomers' hydroscopicity. This detail may be important for reproducing
  the results of Feng et al.

  \begin{figure}[!htb]
  \begin{subfigure}{0.45\textwidth}
  \centering
  % BJC6 : below is the simulated diffraction pattern of the full system. I removed it since showing both
  % makes both patterns small. You can see the full pattern in a separate figure.
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}  
%  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
  \end{subfigure}
  \caption{}\label{fig:rdouble_nophenyls}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{hbonds_tails.png}
  \caption{}\label{fig:hbond_visualization}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds.png}
  \caption{}\label{fig:pore_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
  \caption{}\label{fig:pore_hbonds_ft}
  \end{subfigure}
  \caption{(a) The structure of the head groups is responsible for the appearance of
  R-double. When we remove head groups from the trajectory, the simulated 
  diffraction pattern no longer shows R-double. (b) Monomer head groups above or below
  each other that hydrogen bond with a shared water molecule are drawn closer
  together. Blue monomers were stacked above orange monomers in the initial configuration.
  (c) Monomers in each column are numbered from 1--20. For simplicity, we define a layer to
  be composed of all same-number monomers. Peaks in the distributions indicate
  a shared hydrogen bonded water molecule between a monomer head group and one in the layer
  vertically above it. For example, in Pore 1, monomer 7 shares a hydrogen bond with
  a monomer in layer 8 (pictured in (b)). In this scenario, monomers are no longer evenly
  spaced in the z-direction since they are pulled closer together by hydrogen bonds. 
  (d) We performed discrete fourier transforms on each distribution in (c). In all cases,
  the strongest peak represents periodicity every layer. In Pore 1, there is also periodicity
  every other layer as indicated by the strong peak at 0.5 layers$^{-1}$. In this case, the
  center of mass of two adjacent pairs is separated by twice the average monomer stacking 
  distance, while the four monomers involved are unequally spaced. These conditions may
  give rise to R-double.}\label{fig:hbonds}
  \end{figure}

@@

  %BJC6: moved this paragraph up to make the section more idea-focused
  In general, the composition of each region, particulary within our definition of 
  the pore region, is similar between all systems. We believe we can solvate and study transport
  in any of the systems presented here and extract similar transport mechanisms. We will 
  need to verify that this assumption is true.

@@

  There is a gradient in pore composition transitioning radially from the hydrophilic 
  to the hydrophobic region, rather than an abrupt division. Based on size-exclusion 
  experiments, we define the pore radius to be 0.6 nm
  %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
  ~\cite{zhou_supported_2005}. The system does not confine
  sodium ions and head groups to just within the pore region. For dry systems,
  19\% of sodium ions exist outside the pore region (except sandwiched, ordered basin,
  where 16\% are outside the pore). Additionally, we see that in all cases, about 
  3\% of the plotted tail density is located within the pore region (except ordered sandwiched,
  where 1.5\% are within the pore region). For the solvated system, the results are similar,
  however the head group density is shifted slightly radially outward. This is likely due to
  swelling of the pore by water.

%  These observations bring into question how
%  one should define a pore in these types of systems. One usually measures a 
%  membrane's pore radius based on the size of a molecule it can reject, however
%  it is not clear where the edges of the pores are and what size molecule would
%  fit through. We leave these investigations for a future study.
  %MRS7: or could say that the size could be different depending on the the nature of the molecle. Could bring up
  %Sarah's results with different selectivity of molecules about the same size.

  The space in the pore region is filled with a mixture of sodium ions
  and head groups. The distributions appear somewhat different near r=0, but that noise 
  is expected since there is significantly less sampling as r approaches 0. Regardless, 
  all systems, including the solvated system, have a significant number of head groups 
  and sodium ions occupying the pore center. This observation highlights that the pore
  region is dense, not hollow, and may impede transport of solvent and solutes when
  compared to the previous idealized picture of a hollow tube conducive to transport.
